Further Evidence for Modified Spin-down in Sun-like Stars:\\Pile-ups in the Temperature--Period Distribution

### 2021-12-20 src/ms.tex
paper edits

We determined that 90\% of the stars on the ridge have ages between 1.4--5.6~Gyr (using ages from the CKS catalog), or 2.3--5.9~Gyr (using SPOCS ages). However, we note that systematic effects in surveys and theoretical models lead to large uncertainties in isochrone ages that are not necessarily represented by the reported age uncertainties. In fact, there are only a handful of long-period pile-up stars in the CKS sample with ages older than the age of the Sun, and almost all of the pile-up stars would be compatible with an age equal to or less than the Sun's given the large age uncertainties. The SPOCS ages in particular are questionable given that only $\sim$1\% of the stars have ages $<$~2~Gyr and the concentration of stars at the upper age boundary at a given \teff (Figure~\ref{fig:ages}).

>>>>

We determined that 90\% of the stars on the ridge have ages between 1.4--5.6~Gyr (using ages from the CKS catalog), or 2.3--5.9~Gyr (using SPOCS ages). However, we note that systematic effects in surveys and theoretical models lead to large uncertainties in isochrone ages that are not necessarily represented by the reported age uncertainties. The SPOCS ages in particular are questionable given that only $\sim$1\% of the stars have ages $<$~2~Gyr and the concentration of stars at the upper age boundary at a given \teff (Figure~\ref{fig:ages}). In fact, there are only a handful of long-period pile-up stars in the CKS sample with ages older than the age of the Sun (using CKS ages), and almost all of the pile-up stars would be compatible with an age equal to or less than the Sun's given the large age uncertainties.
